---
title: "Top 30 Country Songs Lyric Analysis"
author: "Dana Gibbon"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    collapsed: true
    toc_depth: 3
    code_folding: hide
    theme: sandstone
    number_sections: false
    highlight: zenburn
---

```{r setup, echo=FALSE, message=FALSE, results='markup', warning=FALSE}
# load libraries 
library(knitr)
library(pander)
library(DT)
library(tidyr)
library(here)
library(tidytext)
library(dplyr)
library(ggplot2)
library(plotly)
library(cowplot)
library(purrr)
library(wordcloud)

# Set up code chunk options
opts_chunk$set(echo = TRUE, message = FALSE, results = 'markup', warning = FALSE)

```

```{r}
# Read in the data
song_list <- read.csv(here("data","songs_top_30.csv"))
song_list <- song_list[1:484,1:8]
# get stop words
data(stop_words)
stop_words <- stop_words %>%
  filter(!(word == "little"))
```

# Summary Tables

## The Number of Top 30 Songs per Artist

```{r}
artist_list <- song_list %>% group_by(Artist) %>% 
  tally() %>% arrange(desc(n)) %>% rename(!!"Songs" := n)
datatable(artist_list,
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

There are `r nrow(artist_list)` different artists with a top 30 song since 2013. Of these artists, only `r artist_list %>% filter(Songs >= 5) %>% nrow()` have had 5 or more top 30 songs.

## The Number of Top 30 Songs per year

```{r}
year_list <- song_list %>% group_by(Entered.Top.30.In.) %>% 
  tally() %>% rename(!!"Songs" := n)
datatable(year_list[-1,],
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

# Specific Word Search {.tabset .tabset-fade}

```{r}
# years
years <- year_list$Entered.Top.30.In.
years <- years[-1]
# words to look for
veh <- c("truck", "pickup", "chevy", "ford", "tacoma", 
         "chevrolet", "tailgate", "car")
cl <- c("jeans", "cutoffs", "jean", "shirt", "hat", 
        "shoe", "dress", "boots")
dr <- c("beer", "drink", "wine", "whiskey", "shots",
        "tequila", "vodka", "margarita", "cocktail", "sippin",
        "alcohol")
bod <- c("eyes", "lips", "hair", "mouth", "hand", 
         "hands", "feet", "chest", "finger", "ears",
         "hips", "legs", "body", "shoulder")
gen <- c("yeah", "night", "tonight", "little", "town",
           "eyes", "eye", "drink", "drinkin", "girl", 
           "boy", "baby", "wanna", "gonna", "road",
           "hand", "kiss", "love", "lovin", "time",
           "heart", "feel", "feeling")
```

```{r}
# Prep df by year
prep_df <- function(df, year){
  songs <- as.character(df$Lyrics)[which(df$Entered.Top.30.In. == year)]
  text_df <- tibble(
    song = as.character(df$Song[which(df$Entered.Top.30.In. == year)]),
    text = songs)
  return(text_df)
}
# function to find a word
search_word <- function(df, term, year, plural=NULL){
  df.y <- prep_df(df, year = year)
  counts.temp <- df.y %>% unnest_tokens(word, text) %>%
    group_by(song) %>% count(word, sort = TRUE)
  counts <- counts.temp %>% 
    filter(word %in% term)
  if(!is.null(plural)){
    for(i in 1:nrow(plural)){
      counts$word <- stringr::str_replace_all(counts$word, plural[i,1], plural[i,2]) 
    }
  }
  counts<- counts %>% 
    tally()
  return(counts)
}

```


## Vehicle {.tabset .tabset-fade}

* Looking for:
    * `r veh`

### Total

```{r}
named <- "vehicle"
veh.l <- lapply(years, function(x){
  search_word(df = song_list, term = veh, year = x)
})
names(veh.l) <- years
vehicle <- do.call(rbind, lapply(veh.l, nrow)) %>% 
  data.frame(row.names = years) %>% 
  `colnames<-`(named)
veh.c <- veh.l %>% map_df(I, .id = "year") %>% 
  as.matrix() %>% data.frame()
datatable(veh.c,
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

### Breakdown

* percentage = % of category, not total songs of the specified year

```{r}
veh.d <- lapply(years, function(x){
  lapply(veh, function(i){
    search_word(df = song_list, term = i, year = x)
  }) %>% `names<-`(veh)
})
names(veh.d) <- years
veh.df <- lapply(1:length(years), function(x){
  bind_rows(veh.d[[x]], .id = "term") %>% 
    group_by(term) %>% tally()
})
names(veh.df) <- years
veh.df <- bind_rows(veh.df, .id = "year")
veh.df$percentage <- 0
veh.df$percentage[veh.df$year == 2014] <- 
  (veh.df$n[veh.df$year == 2014]/vehicle$vehicle[1])*100
veh.df$percentage[veh.df$year == 2015] <- 
  (veh.df$n[veh.df$year == 2015]/vehicle$vehicle[2])*100
veh.df$percentage[veh.df$year == 2016] <- 
  (veh.df$n[veh.df$year == 2016]/vehicle$vehicle[3])*100
veh.df$percentage[veh.df$year == 2017] <- 
  (veh.df$n[veh.df$year == 2017]/vehicle$vehicle[4])*100
veh.df$percentage[veh.df$year == 2018] <- 
  (veh.df$n[veh.df$year == 2018]/vehicle$vehicle[5])*100
veh.df$percentage[veh.df$year == 2019] <- 
  (veh.df$n[veh.df$year == 2019]/vehicle$vehicle[6])*100
veh.df$percentage <- round(veh.df$percentage, 2)
datatable(veh.df,
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```


```{r}
ggplot(veh.df, aes(x = percentage, y = year, fill=term)) + 
  geom_bar(stat="identity", position = "dodge", alpha=1) + 
  theme_bw() + ggtitle("Vehicle Breakdown by Year")

ggplot(veh.df, aes(x = percentage, y = year, fill=term)) + 
  geom_bar(stat="identity", alpha=1) + 
  theme_bw() + ggtitle("Vehicle Breakdown by Year")

```

## Clothes {.tabset .tabset-fade}

* Looking for:
    * `r cl`
    * merged jeans/jean

### Total

```{r}
named <- "clothes"
plural <- rbind(c("jeans", "jean"))
cl.l <- lapply(years, function(x){
  search_word(df = song_list, term = cl, year = x, plural = plural)
})
names(cl.l) <- years
clothes <- do.call(rbind, lapply(cl.l, nrow)) %>% 
  data.frame(row.names = years) %>% 
  `colnames<-`(named)
cl.c <- cl.l %>% map_df(I, .id = "year") %>% 
  as.matrix() %>% data.frame()
datatable(cl.c,
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

### Breakdown

* percentage = % of category, not total songs of the specified year

```{r}
#cl <- cl[-c(1,3)]
cl.d <- lapply(years, function(x){
  lapply(cl[-c(1,3)], function(i){
    search_word(df = song_list, term = i, year = x)
  }) %>% `names<-`(cl[-c(1,3)])
})
names(cl.d) <- years
# deal w/ plurals
cl.d.2 <- lapply(years, function(x){
  search_word(df = song_list, term = cl[c(1,3)], year = x)
})
names(cl.d.2) <- years

cl.df <- lapply(1:length(years), function(x){
  bind_rows(cl.d[[x]], .id = "term") %>% 
    group_by(term) %>% tally()
})
names(cl.df) <- years
temp <- sapply(cl.d.2, nrow)
cl.df.t <- data.frame(year = names(temp),
                      term = "jean(s)",
                      n = temp)

cl.df <- bind_rows(cl.df, .id = "year")

cl.df <- cl.df %>% add_row(cl.df.t)

cl.df$percentage <- 0
cl.df$percentage[cl.df$year == 2014] <- 
  (cl.df$n[cl.df$year == 2014]/clothes$clothes[1])*100
cl.df$percentage[cl.df$year == 2015] <- 
  (cl.df$n[cl.df$year == 2015]/clothes$clothes[2])*100
cl.df$percentage[cl.df$year == 2016] <- 
  (cl.df$n[cl.df$year == 2016]/clothes$clothes[3])*100
cl.df$percentage[cl.df$year == 2017] <- 
  (cl.df$n[cl.df$year == 2017]/clothes$clothes[4])*100
cl.df$percentage[cl.df$year == 2018] <- 
  (cl.df$n[cl.df$year == 2018]/clothes$clothes[5])*100
cl.df$percentage[cl.df$year == 2019] <- 
  (cl.df$n[cl.df$year == 2019]/clothes$clothes[6])*100
cl.df$percentage <- round(cl.df$percentage, 2)
datatable(cl.df,
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```
                   
```{r}
ggplot(cl.df, aes(x = percentage, y = year, fill=term)) + 
  geom_bar(stat="identity", position = "dodge", alpha=1) + 
  theme_bw() + ggtitle("Clothes Breakdown by Year")

ggplot(cl.df, aes(x = percentage, y = year, fill=term)) + 
  geom_bar(stat="identity", alpha=1) + 
  theme_bw() + ggtitle("Clothes Breakdown by Year")

```

## Drinks {.tabset .tabset-fade}

* Looking for:
    * `r dr`

### Total

```{r}
named <- "drinks"
dr.l <- lapply(years, function(x){
  search_word(df = song_list, term = dr, year = x)
})
names(dr.l) <- years
drinks <- do.call(rbind, lapply(dr.l, nrow)) %>% 
  data.frame(row.names = years) %>% 
  `colnames<-`(named)
dr.c <- dr.l %>% map_df(I, .id = "year") %>% 
  as.matrix() %>% data.frame()
datatable(dr.c,
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

### Breakdown

* percentage = % of category, not total songs of the specified year

```{r}
dr.d <- lapply(years, function(x){
  lapply(dr, function(i){
    search_word(df = song_list, term = i, year = x)
  }) %>% `names<-`(dr)
})
names(dr.d) <- years
dr.df <- lapply(1:length(years), function(x){
  bind_rows(dr.d[[x]], .id = "term") %>% 
    group_by(term) %>% tally()
})
names(dr.df) <- years
dr.df <- bind_rows(dr.df, .id = "year")
dr.df$percentage <- 0
dr.df$percentage[dr.df$year == 2014] <- 
  (dr.df$n[dr.df$year == 2014]/drinks$drinks[1])*100
dr.df$percentage[dr.df$year == 2015] <- 
  (dr.df$n[dr.df$year == 2015]/drinks$drinks[2])*100
dr.df$percentage[dr.df$year == 2016] <- 
  (dr.df$n[dr.df$year == 2016]/drinks$drinks[3])*100
dr.df$percentage[dr.df$year == 2017] <- 
  (dr.df$n[dr.df$year == 2017]/drinks$drinks[4])*100
dr.df$percentage[dr.df$year == 2018] <- 
  (dr.df$n[dr.df$year == 2018]/drinks$drinks[5])*100
dr.df$percentage[dr.df$year == 2019] <- 
  (dr.df$n[dr.df$year == 2019]/drinks$drinks[6])*100
dr.df$percentage <- round(dr.df$percentage, 2)
datatable(dr.df,
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

```{r}
ggplot(dr.df, aes(x = percentage, y = year, fill=term)) + 
  geom_bar(stat="identity", position = "dodge", alpha=1) + 
  theme_bw() + ggtitle("Drinks Breakdown by Year")

ggplot(dr.df, aes(x = percentage, y = year, fill=term)) + 
  geom_bar(stat="identity", alpha=1) + 
  theme_bw() + ggtitle("Drinks Breakdown by Year")

```

## Body {.tabset .tabset-fade}

* Looking for:
    * `r bod`
    * merged hand/hands

### Total

```{r}
named <- "body"
plural <- rbind(c("hands", "hand"))
bod.l <- lapply(years, function(x){
  search_word(df = song_list, term = bod, year = x, plural = plural)
})
names(bod.l) <- years
body <- do.call(rbind, lapply(bod.l, nrow)) %>% 
  data.frame(row.names = years) %>% 
  `colnames<-`(named)
bod.c <- bod.l %>% map_df(I, .id = "year") %>% 
  as.matrix() %>% data.frame()
datatable(bod.c,
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

### Breakdown

* percentage = % of category, not total songs of the specified year

```{r}
bod.d <- lapply(years, function(x){
  lapply(bod[-c(5,6)], function(i){
    search_word(df = song_list, term = i, year = x)
  }) %>% `names<-`(bod[-c(5,6)])
})
names(bod.d) <- years
bod.df <- lapply(1:length(years), function(x){
  bind_rows(bod.d[[x]], .id = "term") %>% 
    group_by(term) %>% tally()
})
names(bod.df) <- years
bod.df <- bind_rows(bod.df, .id = "year")

bod.d.2 <- lapply(years, function(x){
  search_word(df = song_list, term = bod[c(5,6)], year = x)
})
names(bod.d.2) <- years
temp <- sapply(bod.d.2, nrow)
bod.df.t <- data.frame(year = names(temp),
                      term = "hand(s)",
                      n = temp)
bod.df <- bod.df %>% add_row(bod.df.t)

bod.df$percentage <- 0
bod.df$percentage[bod.df$year == 2014] <- 
  (bod.df$n[bod.df$year == 2014]/body$body[1])*100
bod.df$percentage[bod.df$year == 2015] <- 
  (bod.df$n[bod.df$year == 2015]/body$body[2])*100
bod.df$percentage[bod.df$year == 2016] <- 
  (bod.df$n[bod.df$year == 2016]/body$body[3])*100
bod.df$percentage[bod.df$year == 2017] <- 
  (bod.df$n[bod.df$year == 2017]/body$body[4])*100
bod.df$percentage[bod.df$year == 2018] <- 
  (bod.df$n[bod.df$year == 2018]/body$body[5])*100
bod.df$percentage[bod.df$year == 2019] <- 
  (bod.df$n[bod.df$year == 2019]/body$body[6])*100
bod.df$percentage <- round(bod.df$percentage, 2)
datatable(bod.df,
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```


```{r}
ggplot(bod.df, aes(x = percentage, y = year, fill=term)) + 
  geom_bar(stat="identity", position = "dodge", alpha=1) + 
  theme_bw() + ggtitle("Body Breakdown by Year")

ggplot(bod.df, aes(x = percentage, y = year, fill=term)) + 
  geom_bar(stat="identity", alpha=1) + 
  theme_bw() + ggtitle("Body Breakdown by Year")

```

## General {.tabset .tabset-fade}

* Looking for:
    * `r gen`

### Total

```{r}
named <- "general"
plural <- rbind(c("eyes", "eye"))
gen.l <- lapply(years, function(x){
  search_word(df = song_list, term = gen, year = x)
})
names(gen.l) <- years
general <- do.call(rbind, lapply(gen.l, nrow)) %>% 
  data.frame(row.names = years) %>% 
  `colnames<-`(named)
gen.c <- gen.l %>% map_df(I, .id = "year") %>% 
  as.matrix() %>% data.frame()
datatable(gen.c,
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

### Breakdown

* percentage = % of category, not total songs of the specified year

```{r}
gen.d <- lapply(years, function(x){
  lapply(gen[-c(6,7)], function(i){
    search_word(df = song_list, term = i, year = x)
  }) %>% `names<-`(gen[-c(6,7)])
})
names(gen.d) <- years
gen.df <- lapply(1:length(years), function(x){
  bind_rows(gen.d[[x]], .id = "term") %>% 
    group_by(term) %>% tally()
})
names(gen.df) <- years
gen.df <- bind_rows(gen.df, .id = "year")

# deal w/ plurals
gen.d.2 <- lapply(years, function(x){
  search_word(df = song_list, term = gen[c(6,7)], year = x)
})
names(gen.d.2) <- years
temp <- sapply(gen.d.2, nrow)
gen.df.t <- data.frame(year = names(temp),
                      term = "eye(s)",
                      n = temp)
gen.df <- gen.df %>% add_row(gen.df.t)

gen.df$percentage <- 0
gen.df$percentage[gen.df$year == 2014] <- 
  (gen.df$n[gen.df$year == 2014]/general$general[1])*100
gen.df$percentage[gen.df$year == 2015] <- 
  (gen.df$n[gen.df$year == 2015]/general$general[2])*100
gen.df$percentage[gen.df$year == 2016] <- 
  (gen.df$n[gen.df$year == 2016]/general$general[3])*100
gen.df$percentage[gen.df$year == 2017] <- 
  (gen.df$n[gen.df$year == 2017]/general$general[4])*100
gen.df$percentage[gen.df$year == 2018] <- 
  (gen.df$n[gen.df$year == 2018]/general$general[5])*100
gen.df$percentage[gen.df$year == 2019] <- 
  (gen.df$n[gen.df$year == 2019]/general$general[6])*100
gen.df$percentage <- round(gen.df$percentage, 2)
datatable(gen.df,
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

```{r}
ggplot(gen.df, aes(x = percentage, y = year, fill=term)) + 
  geom_bar(stat="identity", position = "dodge", alpha=1) + 
  theme_bw() + ggtitle("General Terms Breakdown by Year")

ggplot(gen.df, aes(x = percentage, y = year, fill=term)) + 
  geom_bar(stat="identity", alpha=1) + 
  theme_bw() + ggtitle("General Terms Breakdown by Year")

```

# General Word Search {.tabset .tabset-fade}

## 2014 {.tabset .tabset-fade}

* Removed "stop words"
* Counted the number of songs a specific word occurred in

### Table

```{r}
year <- 2014
tm_2014 <- prep_df(song_list, year = year) %>% unnest_tokens(word, text) %>%
  group_by(song) %>% count(word, sort = TRUE) %>%
  anti_join(stop_words) %>% group_by(word) %>% 
  tally() %>% arrange_at("n", desc)

datatable(tm_2014,
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

### Barplot

```{r,fig.width = 7, fig.height = 7}
tm_2014 %>% top_n(20) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  ylab("Number of Song that Contain the Word") +
  ggtitle("Top 20 Words: 2014") +
  coord_flip() + 
  theme_bw()
```

### Word Cloud

* Top 200 words
* Must have at least 2 occurrences

```{r, fig.width = 8, fig.height = 8}
wordcloud(tm_2014$word, tm_2014$n, scale=c(4,.3), 
          min.freq=2, max.words=200, 
          random.order=T, rot.per=.15,
          colors = brewer.pal(8,"Dark2"),
          vfont=c("sans serif","plain"))

```

## 2015 {.tabset .tabset-fade}

* Removed "stop words"
* Counted the number of songs a specific word occurred in

### Table

```{r}
year <- 2015
tm_2015 <- prep_df(song_list, year = year) %>% unnest_tokens(word, text) %>%
  group_by(song) %>% count(word, sort = TRUE) %>%
  anti_join(stop_words) %>% group_by(word) %>% 
  tally() %>% arrange_at("n", desc)

datatable(tm_2015,
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

### Barplot

```{r,fig.width = 7, fig.height = 7}
tm_2015 %>% top_n(20) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  ylab("Number of Song that Contain the Word") +
  ggtitle("Top 20 Words: 2015") +
  coord_flip() + 
  theme_bw()
```

### Word Cloud

* Top 200 words
* Must have at least 2 occurrences

```{r, fig.width = 8, fig.height = 8}
wordcloud(tm_2015$word, tm_2015$n, scale=c(4,.3), 
          min.freq=2, max.words=200, 
          random.order=T, rot.per=.15,
          colors = brewer.pal(8,"Dark2"),
          vfont=c("sans serif","plain"))

```

## 2016 {.tabset .tabset-fade}

* Removed "stop words"
* Counted the number of songs a specific word occurred in

### Table

```{r}
year <- 2016
tm_2016 <- prep_df(song_list, year = year) %>% unnest_tokens(word, text) %>%
  group_by(song) %>% count(word, sort = TRUE) %>%
  anti_join(stop_words) %>% group_by(word) %>% 
  tally() %>% arrange_at("n", desc)

datatable(tm_2016,
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

### Barplot

```{r,fig.width = 7, fig.height = 7}
tm_2016 %>% top_n(20) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  ylab("Number of Song that Contain the Word") +
  ggtitle("Top 20 Words: 2016") +
  coord_flip() + 
  theme_bw()
```

### Word Cloud

* Top 200 words
* Must have at least 2 occurrences

```{r, fig.width = 8, fig.height = 8}
wordcloud(tm_2016$word, tm_2016$n, scale=c(4,.3), 
          min.freq=2, max.words=200, 
          random.order=T, rot.per=.15,
          colors = brewer.pal(8,"Dark2"),
          vfont=c("sans serif","plain"))

```

## 2017 {.tabset .tabset-fade}

* Removed "stop words"
* Counted the number of songs a specific word occurred in

### Table

```{r}
year <- 2017
tm_2017 <- prep_df(song_list, year = year) %>% unnest_tokens(word, text) %>%
  group_by(song) %>% count(word, sort = TRUE) %>%
  anti_join(stop_words) %>% group_by(word) %>% 
  tally() %>% arrange_at("n", desc)

datatable(tm_2017,
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

### Barplot

```{r,fig.width = 7, fig.height = 7}
tm_2017 %>% top_n(20) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  ylab("Number of Song that Contain the Word") +
  ggtitle("Top 20 Words: 2017") +
  coord_flip() + 
  theme_bw()
```

### Word Cloud

* Top 200 words
* Must have at least 2 occurrences

```{r, fig.width = 8, fig.height = 8}
wordcloud(tm_2017$word, tm_2017$n, scale=c(4,.3), 
          min.freq=2, max.words=200, 
          random.order=T, rot.per=.15,
          colors = brewer.pal(8,"Dark2"),
          vfont=c("sans serif","plain"))

```

## 2018 {.tabset .tabset-fade}

* Removed "stop words"
* Counted the number of songs a specific word occurred in

### Table

```{r}
year <- 2018
tm_2018 <- prep_df(song_list, year = year) %>% unnest_tokens(word, text) %>%
  group_by(song) %>% count(word, sort = TRUE) %>%
  anti_join(stop_words) %>% group_by(word) %>% 
  tally() %>% arrange_at("n", desc)

datatable(tm_2018,
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

### Barplot

```{r,fig.width = 7, fig.height = 7}
tm_2018 %>% top_n(20) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  ylab("Number of Song that Contain the Word") +
  ggtitle("Top 20 Words: 2018") +
  coord_flip() + 
  theme_bw()
```

### Word Cloud

* Top 200 words
* Must have at least 2 occurrences

```{r, fig.width = 8, fig.height = 8}
wordcloud(tm_2018$word, tm_2018$n, scale=c(4,.3), 
          min.freq=2, max.words=200, 
          random.order=T, rot.per=.15,
          colors = brewer.pal(8,"Dark2"),
          vfont=c("sans serif","plain"))

```

## 2019 {.tabset .tabset-fade}

* Removed "stop words"
* Counted the number of songs a specific word occurred in

### Table

```{r}
year <- 2019
tm_2019 <- prep_df(song_list, year = year) %>% unnest_tokens(word, text) %>%
  group_by(song) %>% count(word, sort = TRUE) %>%
  anti_join(stop_words) %>% group_by(word) %>% 
  tally() %>% arrange_at("n", desc)

datatable(tm_2019,
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

### Barplot

```{r,fig.width = 7, fig.height = 7}
tm_2019 %>% top_n(20) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  ylab("Number of Song that Contain the Word") +
  ggtitle("Top 20 Words: 2019") +
  coord_flip() + 
  theme_bw()
```

### Word Cloud

* Top 200 words
* Must have at least 2 occurrences

```{r, fig.width = 8, fig.height = 8}
wordcloud(tm_2019$word, tm_2019$n, scale=c(4,.3), 
          min.freq=2, max.words=200, 
          random.order=T, rot.per=.15,
          colors = brewer.pal(8,"Dark2"),
          vfont=c("sans serif","plain"))

```


# Summary

## Tables {.tabset .tabset-fade}

### Raw Numbers

```{r}
sums <- data.frame(vehicle, clothes, drinks, body)
datatable(sums,
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))

```

### Percentage

* By percentage of top 30 songs per year

```{r}
percent <- round((sums/year_list$Songs[-1])*100, digits = 2)
datatable(percent,
          filter = 'top',
          extensions = 'Buttons',
          options = list(pageLength = 10,
                         dom = 'Bfrtip', 
                         buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```


## Figures

```{r}
percent$year <- rownames(percent)
percent.l <- pivot_longer(percent, 1:(ncol(percent)-1))
percent.l$year <- as.numeric(as.character(percent.l$year))
g <- ggplot(percent.l, aes(x = year, 
                           y = value, color = name)) + 
  geom_point() + geom_line() +
  xlab("Year") + ylab("Percentage of Songs") +
  theme_bw() + ggtitle("Comparison of Categories")
g
ggplotly(g)
```

```{r}
gen.df$year <- as.numeric(as.character(gen.df$year))
p <- ggplot(gen.df, aes(x = year, 
                           y = percentage, color = term)) + 
  geom_point() + geom_line() +
  xlab("Year") + ylab("Percentage of Songs") +
  ggtitle("Comparison of Popular Terms") +
  theme_bw()
p
ggplotly(p)
```




# R-session Information

```{r session.info, echo=FALSE}
capture.output(sessionInfo())
```

